---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# ser

The goal of ser is to automate parts of the SER Communications Committee workflow (e.g. posting to Twitter). This package makes it easier to do so reproducibly and in a place where it is easier for us to collaborate on new automated workflows.

## Installation

You can install the package off of GitHub with:

``` r
# install.packages("remotes")
remotes::install_github("SERTwitter/ser")
```

## What does ser currently do?

ser handles automatic daily tweeting to supplement the work done by content leads and daily email summaries of Twitter activity on the SER account.

* `action_auto_tweet()`
* `action_email_summary()`

ser also provides functions to email summaries of errors that may occur in code while running automatically on the server. `action_safely()` wraps functions to catch errors and email them to an address set by `on_error_email_to()`

```{r, eval=FALSE}
library(ser)
on_error_email_to("your@email.com")

auto_error <- function() {
  stop("this code stopped working")
}

safe_auto_error <- action_safely(auto_error)

# sends an email to stored email address with error message
safe_auto_error()
```

