---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

<!-- badges: start -->
[![Deploy SER script: `auto_meeting_tweet.R`](https://github.com/SERTwitter/ser/workflows/Deploy%20SER%20script:%20%60auto_meeting_tweet.R%60/badge.svg)](https://github.com/SERTwitter/ser/actions)
[![Deploy SER script: `auto_tweet.R`](https://github.com/SERTwitter/ser/workflows/Deploy%20SER%20script:%20%60auto_tweet.R%60/badge.svg)](https://github.com/SERTwitter/ser/actions)
[![Deploy SER script: `collect_twitter_data.R`](https://github.com/SERTwitter/ser/workflows/Deploy%20SER%20script:%20%60collect_twitter_data.R%60/badge.svg)](https://github.com/SERTwitter/ser/actions)
[![Deploy SER script: `deploy_dashboard.R`](https://github.com/SERTwitter/ser/workflows/Deploy%20SER%20script:%20%60deploy_dashboard.R%60/badge.svg)](https://github.com/SERTwitter/ser/actions)
[![Deploy SER script: `email_summary.R`](https://github.com/SERTwitter/ser/workflows/Deploy%20SER%20script:%20%60email_summary.R%60/badge.svg)](https://github.com/SERTwitter/ser/actions)
<!-- badges: end -->

# ser

The goal of ser is to automate parts of the SER Communications Committee workflow (e.g. posting to Twitter). This package makes it easier to do so reproducibly and in a place where it is easier for us to collaborate on new automated workflows.

## Installation

You can install the package off of GitHub with:

``` r
# install.packages("remotes")
remotes::install_github("SERTwitter/ser")
```

## What does ser currently do?

ser handles automatic daily tweeting to supplement the work done by content leads, daily email summaries of Twitter activity on the SER account, posts tweets related to the annual meeting during the three months prior, collects SER-related Twitter data, and deploys a dashboard about SER Twitter activity to shinyapps.io.

* `action_auto_tweet()`
* `action_email_summary()`
* `action_meeting_tweet()`
* `action_deploy_dashboard()`
* `action_collect_twitter_data()`

ser also provides functions to email summaries of errors that may occur in code while running automatically on the server. `action_safely()` wraps functions to catch errors and email them to an address set by `on_error_email_to()`

```{r, eval=FALSE}
library(ser)
on_error_email_to("your@email.com")

auto_error <- function() {
  stop("this code stopped working")
}

safe_auto_error <- action_safely(auto_error)

# sends an email to stored email address with error message
safe_auto_error()
```


## Adding and deploying scripts

Add functions you need for your script in `R/`. Add the script that should be deployed to `inst/scripts` or use `use_ser_script()` to write and open a new script file.

```{r, eval=FALSE}
# do not include `.R` at the end of the name
use_ser_script("script_name")
```


We use GitHub Actions to deploy our scripts. Create a repository under the SERTwitter account. Inside of the repository, run `ser::deploy_ghactions()` with the name of the script to deploy. This will add a DESCRIPTION file and the YAML file you need to deploy to GH Actions

```{r, eval=FALSE}
deploy_ghactions("script_name")
```

## Getting access to the Twitter API

You'll need access to the SER Twitter account. Log in and go to https://developer.twitter.com/en/apps. There, you will find four items you need: the consumer key, consumer secret, access token, and access secret. ser has a function called `ser_token()` that provides a way to access the SER tokens. To do so, you'll need to put them in your .Renviron file. Use the usethis package to open it.

```{r, eval=FALSE}
# Open your .Renviron file
usethis::edit_r_environ()
```

There, you'll need to add the SER tokens. Here, I've put in fake digits. Replace them with the real tokens.

```{r, eval = FALSE}
SER_CONSUMER_KEY=1i2345y6789a
SER_CONSUMER_SECRET=12345d6789b
SER_ACCESS_TOKEN=1g2345678c
SER_ACCESS_SECRET=123r4567f89d
```

Save and restart. Many of the functions in rtweet have a `token` argument. Call `ser_token()` to gain access to the Twitter API:

```{r, eval=FALSE}
rtweet::get_mentions(token = ser_token())
```

## Getting access to Google Drive and Gmail

This is a bit more complicated and requires both API credentials and log-in authorization, meaning you'll need access to the SER Twitter team email address. Contact Malcolm for more information. 
